Assessing linkages between watershed nutrient loading and water quality in a subtropical estuary with semiparametric models.

### 2023-05-20 Schramm-2023-05-AS/Schramm-2023-05-AS.Rmd
fix captions

```{r fig3, error=FALSE, warning=FALSE, message=FALSE, fig.width=6.85, fig.asp=0.7, fig.cap="Aggregated estimated annual and flow-normalized annual NO~3~ and TP loads for USGS-08164000 and USGS-08164525."}

@@

```{r fig6, message=FALSE, warning=FALSE, fig.width=6.85, fig.asp=0.7, fig.cap="Estimated effects of mean daily inflow residuals on mean TP, NO~*x*~, chlorophyll-*a*, TKN, and DO concentrations in Lavaca Bay obtained from flow estuary GAMs."}

@@

```{r fig7, message=FALSE, warning=FALSE, fig.width=6.85, fig.asp=0.45, fig.cap="Estimated effects of nutrient load residuals on TP and NO~*x*~ concentrations in Lavaca Bay obtained from flow+load estuary GAMs."}

>>>>

```{r fig3, error=FALSE, warning=FALSE, message=FALSE, fig.width=6.85, fig.asp=0.7, fig.cap="Aggregated estimated annual and flow-normalized annual NO\\textsubscript{3} and TP loads for USGS-08164000 and USGS-08164525."}

@@

```{r fig6, message=FALSE, warning=FALSE, fig.width=6.85, fig.asp=0.7, fig.cap="Estimated effects of mean daily inflow residuals on mean TP, NO\\textsubscript{\\textit{x}}, chlorophyll-\\textit{a}, TKN, and DO concentrations in Lavaca Bay obtained from flow estuary GAMs."}

@@

```{r fig7, message=FALSE, warning=FALSE, fig.width=6.85, fig.asp=0.45, fig.cap="Estimated effects of nutrient load residuals on TP and NO\\textsubscript{\\textit{x}} concentrations in Lavaca Bay obtained from flow+load estuary GAMs."}

### 2023-05-20 Schramm-2023-05-AS/Schramm-2023-05-AS.tex
fix captions

\caption{Aggregated estimated annual and flow-normalized annual NO~3~ and TP loads for USGS-08164000 and USGS-08164525.}\label{fig:fig3}
\end{figure}

@@

\caption{Estimated effects of mean daily inflow residuals on mean TP, NO~*x*~, chlorophyll-*a*, TKN, and DO concentrations in Lavaca Bay obtained from flow estuary GAMs.}\label{fig:fig6}
\end{figure}

@@

\caption{Estimated effects of nutrient load residuals on TP and NO~*x*~ concentrations in Lavaca Bay obtained from flow+load estuary GAMs.}\label{fig:fig7}
\end{figure}

>>>>

\caption{Aggregated estimated annual and flow-normalized annual NO\textsubscript{3} and TP loads for USGS-08164000 and USGS-08164525.}\label{fig:fig3}
\end{figure}

@@

\caption{Estimated effects of mean daily inflow residuals on mean TP, NO\textsubscript{\textit{x}}, chlorophyll-\textit{a}, TKN, and DO concentrations in Lavaca Bay obtained from flow estuary GAMs.}\label{fig:fig6}
\end{figure}

@@

\caption{Estimated effects of nutrient load residuals on TP and NO\textsubscript{\textit{x}} concentrations in Lavaca Bay obtained from flow+load estuary GAMs.}\label{fig:fig7}
\end{figure}
